Sequence Specific Modeling of \emph{E.~coli} Cell-Free Protein Synthesis

### 2017-04-20 Paper_v1.tex
Updated the KO figure

\subsection*{Identification of potential alternative optimal metabolic flux solutions.}
We identified potential alternative optimal metabolic flux distributions by performing single and pairwise reaction group knockout simulations [TODO:REF].
Reaction group knockouts were simulated by setting the flux bounds for all the reactions involved in a group to zero.
We grouped reactions in the cell-free network into 19 subgroups (available in Supporting Information).
We computed the difference ($l^{2}$-norm) for CAT productivity in the presence and absence of pairwise reaction knockouts.
Simultaneously, we computed the difference in the flux distribution ($l^{2}$-norm) for each pairwise reaction knockout compared to the flux distribution with no knockouts.
Those solutions with the same or similar productivity but large changes in the metabolic flux distribution represent alternative optimal soluations.

>>>>

\subsection*{Potential alternative optimal metabolic flux solutions.}
We identified potential alternative optimal metabolic flux distributions by performing single and pairwise reaction group knockout simulations [TODO:REF].
Reaction group knockouts were simulated by setting the flux bounds for all the reactions involved in a group to zero.
We grouped reactions in the cell-free network into 19 subgroups (available in Supporting Information).
We computed the difference ($l^{2}$-norm) for CAT productivity in the presence and absence of pairwise reaction knockouts.
Simultaneously, we computed the difference in the flux distribution ($l^{2}$-norm) for each pairwise reaction knockout compared to the flux distribution with no knockouts.
Those solutions with the same or similar productivity but large changes in the metabolic flux distribution represent alternative optimal soluations.
